---
title: "Functions for Cleaning, Exporting, Summarising and Plotting the GLAD Data"
output:
  html_document:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{GLAD Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA,
  results = "asis",
  prompt = FALSE,
  cache = FALSE,
  message = FALSE,
  warning = FALSE,
  echo = TRUE
)
# googlesheets4 option, see https://gargle.r-lib.org/articles/non-interactive-auth.html
options(gargle_oauth_email = TRUE)
```

```{r setup}
library(gladfunctions)
```

## Cleaning Qualtrics Exports

Specify the path to the directory containing the raw files exported
directly from Qualtrics. This must contain the sign-up data and if an
optional questionnaire is to be cleaned, the data of that optional
questionnaire. We have a `python` script for exporting Qualtrics data,
please speak to Henry Rogers in the BioResource office.

```{r, raw path}
raw_path <- "../../../../Research/Data/GLAD/GLAD-Questionnaires-Cleaning/data_raw/"
```

Specify the path to export files to.

```{r, clean path}
clean_path <- "../../../../Research/Data/GLAD/GLAD-Questionnaires-Cleaning/data_clean/"
```

Read in data file as a list from raw_path.

```{r read data, eval = FALSE}
dat_list <- GLAD_rawall(raw_path)
```

Clean all the questionnaire and export to clean_path.

```{r clean all, eval = FALSE}
GLAD_cleanall(dat_list)
```

Clean a specified questionnaire and export to clean_path.

```{r clean specified questionnaire, eval = FALSE}
GLAD_clean("CIDID", dat_list)
```

Select variables to export with Easy.name

```{r select variables, eval = FALSE}
PAD <-
  readRDS(paste(clean_path, "rds_renamed/PAD_Renamed.rds", sep = "/"))
which <- colnames(PAD)[10:15]

GLAD_select(PAD, which, sheet)
```

## Read in the data file and dictionary sheet

`rds` is a fast loading file format that preserves variable type
information that can be read like a csv.  I'm reading in the "_Renamed"
version with easy names, but note that all the following should also work
for unrenamed version ( with "New.variable" names)

```{r read in data files}
PAD <-
  readRDS(paste(clean_path, "rds_renamed/PAD_Renamed.rds", sep = "/"))

sheet <- GLAD_sheet("PAD")
```

## Add derived variables to data

```{r add derived variables}
PAD <- GLAD_derive(PAD, sheet)
```

## Quantile Plot

```{r vartest, results = "markup"}
GLAD_qplot(data = PAD, var = "pad.frequency_panic_attacks")
```

## Variance Test

```{r, results = "markup"}
# Note the use of `resuls = "mark up"` here. I am overwriting
# `results = "asis"` at the start of the script.
# "asis" writes text outputs from `summarytools` and
# `kable` to markdown format (so that they display nicely). Here we just
# need the output of these tests remain as plain text.

GLAD_vartest(data = PAD, var = "pad.frequency_panic_attacks", googlesheet = sheet)
```

For quantile plot and variance test, I also have a version that extracts
all the continuous variables and loops through them.  Would that be more
desirable?

## Missingness

```{r missingness}
missingness <- GLAD_missing(data = PAD)
 ```

```{r missingness percent, results = "markup"}
missingness$percent
 ```

```{r missingness descr}
missingness$descr
```

```{r missingness freq}
missingness$freq
```

A value of '1' for a variable in the left most column indicates which
missing percentage it has.

```{r missingness table}
print(missingness$table)
```

```{r missingness plot, fig.width = 10, fig.height = 10}
missingness$plot
```

## Plots

 ```{r sex plot, fig.width = 10}
# Use `fig.width` to avoid the figure being truncated.
GLAD_plot(data = PAD, var = "Sex", googlesheet = sheet)
```

```{r factor_plots, fig.width = 13}
GLAD_plot(
  data = PAD,
  var = "pad.anx_future_panic_attacks",
  googlesheet = sheet
)
```

Note that `continuous_plots` also takes a logical argument `include_outlier`.
For variables that don't have maximum or minimum in the dictionary hence haven't been cleaned,
this is useful for deciding cut-offs.

Set `binwidth = "FD"` to apply the Freedman-Diaconis rule for deciding
optimal binwidth. The default is one and should be suitable for most
variables in the data sets.

```{r continuous_plots}
continuous_plots <- GLAD_plot(
  data = PAD,
  var = "pad.frequency_panic_attacks",
  googlesheet = sheet,
  include_outlier = TRUE,
  binwidth = "FD"
)
```

```{r continuous_plots_point}
continuous_plots$point
```

```{r continuous_plots_hist}
continuous_plots$hist
```

```{r continuous_plots_density}
continuous_plots$density
```

```{r continuous_densitybysex}
continuous_plots$densitybysex
```

This plot is for categorical variables that allow multiple options to be selected.
Put in one of the variables representing the options. Don't seem to have a
generalized way to extract the tile from the dictionary. Specify the title yourself.

```{r categorical_plot, fig.width = 10, fig.height = 10}
GLAD_plot(
  data = PAD,
  var = "pad.sweating",
  title = "title",
  googlesheet = sheet
)
```
